Scaling up the hyperparameter grid for Naomi

### 2023-03-02 src/naomi-simple_fit/aghq-grid-scale-up.Rmd
Eigendecomposition approach for smaller grid

>>>>

What about using the eigenvalues rather than the standard deviation?

```{r}
m <- sd_out$par.fixed
C <- sd_out$cov.fixed
E <- eigen(C)
V <- diag(E$values)
D <- E$vectors
```

The relative contributions of each dimension (similar to a Scree plot) are as follows:

```{r}
tv_df <- data.frame(
  n = 1:length(E$values),
  tv = cumsum(E$values / sum(E$values))
)

ggplot(tv_df, aes(x = n, y = tv)) +
  geom_point() +
  geom_hline(yintercept = 0.9, col = "grey", linetype = "dashed") +
  annotate("text", x = 20, y = 0.875, label = "90% of total variation explained", col = "grey") +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Dimensions of PCA included", y = "Total variation explained") +
  theme_minimal()
```

```{r}
create_grid <- function(d, k) {
  mvQuad::createNIGrid(dim = d, type = "GHe", level = k)
}

gg <- create_grid(d = 24, k =)
```

```{r}
#' @param gg Quadrature grid
#' @param D Eigenvectors of the Hessian
#' @param V Eigenvalues of the Hessian
#' @param m Mode
#' @param p The number of dimensions of the PCA included
pca_rescale_grid <- function(gg, D, V, m, p) {
  d <- dim(D)[1]

  Dp <- sparseMatrix(
    i = rep(1:p, times = p),
    j = sort(rep(1:p,times = p)),
    x = as.numeric(D[1:p, 1:p]),
    dims = c(d, d)
  )

  Vp <- Diagonal(n = d, x = c(sqrt(diag(V)[1:p]), rep(0, (d - p))))
  DVp <- Dp %*% Vp

  newnodes <- t(DVp %*% t(mvQuad::getNodes(gg)))
  for(j in 1:d) newnodes[ ,j] <- newnodes[ ,j] + m[j]
  newweights <- sqrt(det(V)) * mvQuad::getWeights(gg)

  list(nodes = newnodes, weights = newweights)
}
```

```{r}
gg5 <- pca_rescale_grid(gg = create_grid(d = 24, k = 2), D = D, V = V, m = m, p = 5)
gg7 <- pca_rescale_grid(gg = create_grid(d = 24, k = 2), D = D, V = V, m = m, p = 7)
gg7 <- pca_rescale_grid(gg = create_grid(d = 24, k = 2), D = D, V = V, m = m, p = 9)

out <- as.data.frame(as.matrix(gg$nodes))
out$lps <- -1 * apply(out, 1, fit$obj)
out$w <- gg$weights
logSumExpWeights(out$lps, out$w)
```
